---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Lifecycle: deprecated](https://img.shields.io/badge/lifecycle-deprecated-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#deprecated)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)


## Introduction

`filer` is an R package read and write bulk files as a named list of objects.
The user can supply custom read and write functions.

## Utilisation

```{r}
library(filer)

objects <- read_files(system.file("extdata", package = "filer"))
objects
```

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/filer)
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/filer")
```

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("filer")
```

## Citation

```{r, comment="", echo=FALSE}
citation(package = "filer")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/filer/issues).

[Pull requests](https://github.com/poissonconsulting/filer/pulls) are always welcome.

## Code of Conduct

Please note that the filer project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

